Negative and Fractional Types

### 2012-06-26 rational_ext.tex
nothing really

In order to interpret fractional types, we define a monad {{S}} over the
{{Pi}}-category of finite sets and bijections. The functor part of the monad
\[\begin{array}{rcl}

\end{array}\]

\paragraph*{Data.} We extend values types with types {{S b}} denoting sets of
values {{ {| v1, v2, dots |} }}:
%subcode{bnf} include main
% value types, b ::= 0 | 1 | b + b | b * b | S b
% values, v ::= () | left v | right v | (v, v) | {| v1, v2, dots |}

>>>>

In order to interpret fractional types, we first define a monad {{S}} over
the {{Pi}}-category of finite sets and bijections.

\paragraph*{Data.} The syntax of {{Pi}} is extended with the type {{S b}}
which denotes sets {{ {| v1, v2, dots |} }} of values of type {{b}}:
%subcode{bnf} include main
% value types, b ::= 0 | 1 | b + b | b * b | S b
% values, v ::= () | left v | right v | (v, v) | {| v1, v2, dots |}
